%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Scott}{Morgan}
%\title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
%\address{51 Gregory Close, Pencoed, Bridgend, CF35 6RF}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
%\phone[mobile]{+44 7725 131355}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{MorganSN@cardiff.ac.uk}                               % optional, remove / comment the line if not wanted
\homepage{scott3142.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{A dedicated and committed individual with a strong passion for education, teaching and learning.}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

%packages added by me
\usepackage{eurosym}
\usepackage{amstext} % for \text
\DeclareRobustCommand{\officialeuro}{%
  \ifmmode\expandafter\text\fi
  {\fontencoding{U}\fontfamily{eurosym}\selectfont e}}

\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\small{A dedicated and committed individual with a strong passion for education, teaching and learning.}

\section{Education}

\vspace{10pt}

\subsection{Academic Qualifications}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2014--Present}{PhD Mathematics: \textit{In Progess}}{Cardiff University}{}{}{}}

\item{\cventry{2010--2014}{MMath Mathematics: First Class Honours, Best in School}{Cardiff University}{}{}{}}

\item{\cventry{2008--2010}{A levels: \textit{Mathematics (A*), Further Mathematics (A), Physics (A), French (A), Spanish (A)}}{Pencoed Comprehensive School}{}{}{}}  % arguments 3 to 6 can be left empty

\end{itemize}

\vspace{10pt}

\subsection{Research Projects}

\vspace{5pt}

\begin{itemize}

\item{\textbf{PhD Thesis (In Progress):} \textit{Stability of Oscillatory Rotating Disk Boundary Layers}

\vspace{3pt}

\small{\textit{Supervisor: Dr. Chris Davies \\
Synopsis: To investigate the stabilising effects of adding modulation to a rotating disk boundary layer.}}}

\vspace{10pt}

\item{\textbf{MMath Thesis:} \textit{Topics in Oscillatory Flow}

\vspace{3pt}

\small{\textit{Supervisor: Dr. Chris Davies \\
Synopsis: To investigate the connection between the local and global stability analyses of an oscillatory Stokes layer.}}}

\vspace{10pt}

\item{\textbf{Undergraduate Project (CUROP): }\textit{Boundary Layer Flows with an Oscillatory Rotation Rate}

\vspace{3pt}

\small{\textit{Supervisor: Dr. Chris Davies \\
Synopsis: To develop an efficient numerical algorithm for solving a system of nonlinear time-dependent differential equations.}}}

\end{itemize}

\vspace{10pt}

\subsection{Academic Awards}

\vspace{5pt}

\begin{itemize}

\item{\textbf{Recognition for Outstanding Contribution (2017)} - \small{\textit{Society for Industrial and Applied Mathematics}}}

\vspace{6pt}

\item{\textbf{Best in School Prize (2014)} - \small{\textit{Cardiff University}}}

\vspace{6pt}

\item{\textbf{Second Year Prize (2013)} - \small{\textit{Cardiff University}}}

\vspace{6pt}

\item{\textbf{First Year Prize (2012)} - \small{\textit{Cardiff University}}}

\vspace{6pt}

\item{\textbf{Calculus Prize (2011)} - \small{\textit{Cardiff University}}}

\vspace{6pt}

\item{\textbf{Headteacher's Award (2010)}  - \small{\textit{Pencoed Comprehensive School}}}

\end{itemize}

\newpage

\subsection{Notable Contributions}

\vspace{5pt}

\begin{itemize}

\item{\textbf{Founding member of UKFN SIG on boundary layers and complex rotating flows} \textit{(2017)}

\vspace{6pt}

}

\item{\textbf{Cardiff SIAM-IMA Student Chapter President} \textit{(2015-2017)}

\vspace{6pt}

\small{
\begin{itemize}
	\item \textbf{May 2016} - Organised and hosted the SIAM National Student Chapter Conference at Cardiff University. Responsible for arranging programme, lunch and inviting speakers. Over 50 attendees and consisted of parallel student sessions together with plenary talks.
	\vspace{6pt}
	\item \textbf{August 2016} - Oversaw re-branding of new SIAM-IMA Student Chapter from SIAM Chapter after securing funding from the IMA.
	\vspace{6pt}
	\item \textbf{October 2016 - Present} - Arranged highly successful, weekly \textit{popular science} talks delivered by and to postgraduate students.
	\vspace{6pt}
	\item \textbf{April 2017} - Organised \textit{3-minute thesis} competition for postgraduate students. Responsible for organisation, lunch and prizes. Attended by 20 students.
	\vspace{6pt}
	\item \textbf{June 2017} - Organised several workshop sessions including robotics, 3D printing and Raspberry Pi for FE College students at the University. Secured funding from the IMA via an Education Grant and from the University's Widening Access Fund. Event took place over one day and was attended by over 75 students and staff.
\end{itemize}
}}

\vspace{6pt}

\item{\textbf{Lead Instructor on Final-Year MATLAB Course} \textit{(2017)}

\vspace{6pt}

\small{
\begin{itemize}
	\item Devised, composed and delivered an 11-week intensive course titled \textit{An Introduction to MATLAB} to final-year undergraduates and postgraduates. Responsible for all aspects of the course.
\end{itemize}
}}


\vspace{6pt}

\item{\textbf{Raspberry Pi Certified Educator} \textit{(2017)}

\vspace{6pt}

\small{
\begin{itemize}
	\item Successful application to attend two-day course on using Raspberry Pi computers for education. Active member of the Raspberry Pi community and have contributed to educational resources which have been actively used in schools and colleges in England and Wales.
\end{itemize}
}}


\vspace{6pt}

%\item{\textbf{Student-Staff Panel Undergraduate Representative} \textit{(2010-2011)}

%\vspace{6pt}

%\small{
%\begin{itemize}
%	\item Involved in policy and decision-making for the department as an undergraduate. Representative for 170 students.
%\end{itemize}
%}}

\end{itemize}

\section{Professional Experience}

\vspace{6pt}

\begin{itemize}

\item{\cventry{October 2014--Present}{Postgraduate Demonstator}{Cardiff University}{}{}{\vspace{3pt}
\begin{itemize}
\item Led weekly classroom based tutorial sessions on a wide variety of topics including Calculus, Group Theory, Analysis, Differential Equations and Computing.
\vspace{3pt}
\item Instructor in weekly drop-in sessions, handling a wide range of mathematics-based queries from students in many fields including Engineering, Physics, Economics, Biology and Chemistry.
\end{itemize}
}}

\vspace{6pt}

\item{\cventry{September 2016--Present}{Computing Advisor and Associate Lecturer}{Bridgend College}{}{}{\vspace{3pt}
\begin{itemize}
\item Devised, composed and delivered units for BTEC Levels 2-4 modules in Automated Systems, Control Systems and Website Design and Development.
\vspace{3pt}
\item Delivered training sessions to staff at Bridgend College using Raspberry Pi and Python.
\vspace{3pt}
\item Engaged with students via classes and workshops and provided technical assistance with teaching and project based modules.
\vspace{3pt}
\item Worked closely with PiCymru and participated in regional and national  events such as the Urdd Eisteddfod, World Skills Cymru and STEM fairs to showcase projects to local schools and businesses.
\end{itemize}
}}

\end{itemize}

\section{Funding Received}

\vspace{6pt}

\begin{itemize}

\item \textbf{EPSRC Postgraduate Research Studentship} \textit{(2014-2018)} \\
\textit{£13,863 p/a (3.5 years)}

\vspace{6pt}

\item \textbf{SIAM UKIE Student Travel Award} \textit{(2019)}\\
\textit{£80}

\vspace{6pt}

\item \textbf{SIAM Student Travel Award} \textit{(2017)}\\
\textit{\$800}

\vspace{6pt}

\item \textbf{ERCOFTAC PhD Scholarship for Conference Attendance} \textit{(2017)}\\
\textit{\euro{}220}

\vspace{6pt}

\item \textbf{SIAM Student Representative Award} \textit{(2016)}\\
\textit{\$700}

\vspace{6pt}

\item \textbf{Cardiff Undergraduate Research Opportunities Program (CUROP)} \textit{(2013)} \\
\textit{£1600 (8 weeks)}

\vspace{6pt}

\item \textbf{IMA Education Grant} \textit{(on behalf of SIAM-IMA Student Chapter)} \textit{(2017)}\\
\textit{£400}

\vspace{6pt}

\item \textbf{Cardiff University Widening Access Grant} \textit{(on behalf of SIAM-IMA Student Chapter)} \textit{(2017)}\\
\textit{£300}

\vspace{6pt}

\end{itemize}

\section{Conferences \& Workshops}

\vspace{6pt}

\begin{itemize}

\item{\textbf{Hosted:}
\begin{itemize}
\vspace{3pt}
\item SIAM-IMA Chapter \textit{Full STEAM Ahead} Workshops - \textit{Cardiff University (2017)}
\vspace{3pt}
\item 5th SIAM National Student Chapter Conference - \textit{Cardiff University (2016)}
\end{itemize}}

\vspace{6pt}

\item{\textbf{Invited Talk:}
\begin{itemize}
\vspace{3pt}
\item Department of Engineering Seminar Series - \textit{Leicester (2017)}
\vspace{3pt}
\end{itemize}}


\vspace{6pt}

\item{\textbf{Contributed Talk:}
\begin{itemize}
\vspace{3pt}
\item DiPaRT - \textit{Bristol (2017)}
\vspace{3pt}
\item UKFN SIG: Boundary layers and complex rotating flows - \textit{Warwick (2017)}
\vspace{3pt}
\item SIAM Annual Meeting - \textit{Pittsburgh (2017)}
\vspace{3pt}
\item ERCOFTAC SIG33 Workshop on Progress in Flow Instability, Transition
and Control - \textit{Siena (2017)}
\vspace{3pt}
\item 6th SIAM National Student Chapter Conference - \textit{Galway (2017)}
\vspace{3pt}
\item Welsh Mathematics Colloquium - \textit{Gregynog (2017)}
\vspace{3pt}
\item 5th SIAM National Student Chapter Conference - \textit{Cardiff University (2016)}
\vspace{3pt}
\item Welsh Mathematics Colloquium - \textit{Gregynog (2016)}
\vspace{3pt}
\item Applied Mathematics Research Workshop - \textit{Cardiff University (2015)}
\end{itemize}}

\vspace{6pt}

\item{\textbf{Contributed Poster:}
\begin{itemize}
%\vspace{3pt}
\item SIAM UKIE Annual Meeting - \textit{University of Southampton (2018)}
%\item 5th SIAM National Student Chapter Conference - \textit{Cardiff University (2016)}
\vspace{3pt}
\item SIAM UKIE 20th Annual Meeting - \textit{University of Cambridge (2016)}
\end{itemize}}

\vspace{6pt}

\item{\textbf{Wokshops Attended}:
\begin{itemize}
%\vspace{3pt}
%\item Initial Meeting of UKFN SIG on Complex Boundary Layers \& Rotating Flows - \textit{Cambridge (2017)}
%\vspace{3pt}
%\item DiPaRT - \textit{Bristol (2016)}
\vspace{3pt}
\item Research Software Development Workshop - \textit{Cardiff University (2018)}
\vspace{3pt}
\item Fortran Modernisation Workshop - \textit{Warrington (2016)}
\vspace{3pt}
%\item SIAM Annual Meeting - \textit{Boston (2016)}
%\vspace{3pt}
%\item Welsh Mathematics Colloquium - \textit{Gregynog (2015)}
%\vspace{3pt}
%\item SIAM Student Chapter Conference - \textit{Cardiff University (2015)}
%\vspace{3pt}
%\item 4th Joint BAMC \& BMC - \textit{University of Cambridge (2015)}
%\vspace{3pt}
%\item BAMC - \textit{Cardiff University (2014)}
\end{itemize}}

\vspace{6pt}

\end{itemize}

%\newpage

%\section{Technical Skills}

%\vspace{6pt}

%\begin{itemize}

%\item \textbf{Programming \& Software:}
%\begin{itemize}
%\vspace{3pt}
%\item Proficient in: MATLAB, Fortran, Python, TeX, HTML, PHP, CSS, git, bash
%\vspace{3pt}
%\item Basic ability with: Mathematica, C++, JavaScript
%\end{itemize}

%\vspace{6pt}

%\item \textbf{Other:}
%\begin{itemize}
%\vspace{3pt}
%\item Excellent oral and written communication skills from extensive report writing and discussion of my work with a large variety of people.
%\vspace{3pt}
%\item Strong interpersonal skills due to extensive teaching experience.
%\vspace{3pt}
%\item Highly developed organisational skills acquired from organising conferences and student events.
%\end{itemize}

%\vspace{6pt}

%\end{itemize}

\section{References}

\vspace{6pt}

\begin{itemize}

\item{Available on request}

\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
